\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Jordan M. Navarro}
\address{8040 Rowland Ave Apt C154 \\ Philadelphia, PA 19136}
\address{215~$\cdot$~668~$\cdot$~2088 \\ https://navarroj.me \\ thejnav@protonmail.com}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf Carleton College} \hfill {Northfield, Minnesota} \\ 
    {Bachelor of Arts} \hfill {Anticipated June 2022}
  \end{rSection}
  
  \begin{rSection}{Experience}  
    \begin{rSubsection}{Carleton College DataSquad}{Northfield, Minnesota}{Student Squad Member}{September 2018 - April 2019}
    \item Analyzed data sets to determine their usability in separate conditions.
	\item Assisted customers with issues regarding the Moodle learning management system (LMS).
	\item Ghostwrote articles for employee blog sites.
    \item Managed individual and team blogs centered around data related projects.
    \end{rSubsection}
  
    \begin{rSubsection}{PECO Energy Company}{Philadelphia, Pennsylvania}{Information Technology Contractor}{September 2017 - May 2018}
	\item Documented job aids for various applications and standard operating procedures.
    \item Operated electronic document management system (EDMS) to meticulously track revisions within shared documents and documentation for standard operating procedures.
	\item Prepared electricity meters to measure customer electrical energy usage data.
    \item Recorded generated downtime reports into system downtime application.
    \end{rSubsection}

    \begin{rSubsection}{TD Bank, N.A.}{Mount Laurel, New Jersey}{Contractor}{September 2014 - May 2017}
	\item Maintained spreadsheets which contained sensitive employee information.
	\item Measured growth and decline in efficiency, upon completion of tasks, between separate departments.
	\item Packaged data reports and submitted them for delivery to separate customers.
    \item Processed credit references for customers.
    \end{rSubsection}  
  \end{rSection}
  
  \begin{rSection}{Extracurricular Activities}    
    \begin{rSubsection}{Carleton College Winter Ambassador Program}{Northfield, Minnesota}{Student Ambassador}{December 2018 - January 2019}
	\item Prepared presentation which introduced Carleton College and differentiated liberal arts colleges \& research universities and presented it to students at high school.
    \end{rSubsection}
  \end{rSection}
  
  \begin{rSection}{Skills \& Interests}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer & CSS3, Fiddler, G Suite, HTML5, JavaScript, LaTeX, LibreOffice Suite, \\
	  & Microsoft Office Suite, Python, R \\
      Languages & Latin (Intermediate) \\
	  Interests & Computer Science, Economics, Philosophy, Statistics
    \end{tabular}
  \end{rSection}
 
\end{document}